---
title: "LEGO"
format: 
  html:
    embed-resources: true
---

### Packages

We will use the **tidyverse** package for the majority of data wrangling and visualization tasks. The __tidyverse__ can be loaded with the following command:

```{r}
#| label: load-packages
#| message: false
library(tidyverse)
```

## Data

The data is contained in the file `lego.csv` and can be found on Moodle in the folder *Data files, Quarto files and Solutions to previous problem sets*.

It is simulated data based on real prices for LEGO sales in 2018 in the United States. Names and hobbies have been randomly generated. The dataset contains the following variables.

| Variable    | Description |
| -------- | ------- |
| `first_name` | First name of customer |
| `last_name` | Last name of customer |
| `age`  | Age of customer |
| `phone_number` | Phone number of customer |
| `set_id` | Set ID of LEGO set purchased | 
| `number` | Item number of LEGO set purchased |
| `theme` | Theme of LEGO set purchased |
| `subtheme` | Sub theme of LEGO set purchased |
| `year` | Year of purchase |
| `name` | Name of LEGO set purchased |
| `pieces` | Number of pieces of LEGOs in set purchased |
| `us_price` | Price of the set purchased in US Dollars |
| `quantity` | Quantity of LEGO set(s) purchased |



## Solutions




::: {#sol-1}

Save the data and the starter file appropriately so the following code works.



```{r}
#| label: readin-data
#| message: false
#| eval: false
lego <- read_csv("data/lego.csv")
```

  *Remark:* Don't forget to remove `eval: false` or change it to  `eval: true`.

  Take a glimpse at the data.

```{r}
#| eval: false
lego
```

:::  




::: {#sol-2}

Remove this text, and add your answer for Exercise 2 here. Complete the given R code. Remove 
the chunk option `eval: false`.


```{r}
#| eval: false
lego |> 
  
```



:::  






::: {#sol-3}

Remove this text, and add your answer for Exercise 3 here. Complete the given R code. Remove 
the chunk option `eval: false`.

```{r}
#| eval: false
lego <- lego |> 
  drop_na(___)
```


:::  



::: {.callout-important icon=false}

# Note

Use the reduced dataset for all subsequent questions.


:::





::: {#sol-4}
Remove this text, and add your answer for Exercise 4 here. Complete the given R code. Remove 
the chunk option `eval: false`.


```{r}
#| eval: false
lego |> 
  group_by(theme) |>
  
```

You can solve the task in two steps

```{r}

```



:::  







::: {#sol-5}

Remove this text, and add your answer for Exercise 5 here. Complete the given R code. Remove 
the chunk option `eval: false`.

```{r}
#| eval: false
lego <- lego |> 
  mutate(age_group = ___ )
```
:::  




::: {#sol-6}

Remove this text, and add your answer for Exercise 6 here. Complete the given R code. Remove 
the chunk option `eval: false`.



```{r}
#| eval: false
lego |> 
  group_by(___) |>
  
```

:::  









::: {#sol-7}
Remove this text, and add your answer for Exercise 7 here. Complete the given R code. Remove 
the chunk option `eval: false`.


```{r}
#| label: theme-age-dependence-2
#| eval: false
lego |> 
  filter( ___ ) |> 
  ggplot(aes(x = ___, ___)) +
  

```



Between the variables `theme` and `age_group`....
:::  






::: {#sol-8}
Remove this text, and add your answer for Exercise 8 here. Complete the given R code. R



```{r}



```

:::  




::: {#sol-9}
Remove this text, and add your answer for Exercise 9 here. Complete the given R code.



```{r}

```

:::  

