---
title: "Solution to HW problem - Nobel laureates"
format: 
  html:
    embed-resources: true
---



### Packages

We'll use the **tidyverse** package in this homework problem.
Therefore,  let's load this collection of packages by the following command:

```{r}
#| label: load-packages
#| message: false
library(tidyverse)
```

### Data

The dataset for this assignment can be found as a CSV (_comma separated values_) file in the Moodle folder "Data files, Quarto files and Solutions to previous problem sets". 
Create a subfolder with the name' data' in the folder where you have saved this file (`starter_nobel_laureates.qmd`) and save the CSV file `nobel-2023.csv` to this subfolder. Then, use the following command to read (using the `read_csv()` function from the `readr` package) in the data.


```{r}
#| label: load-data
#| message: false
#| eval: false
nobel <- read_csv("data/nobel-2023.csv")
```



> Don't forget to remove the chunk option `eval: false`. Otherwise, the code will not be evaluated.


The variable descriptions are as follows:

- `year`: The year in which the Nobel Prize was awarded
	

- `category`: The category of the Nobel Prize
	

- `motivation`: The reason or motivation for awarding the Nobel Prize to the laureate
	

- `prize_share`: The share of the prize received by the laureate
	

- `laureate_id`: Unique identifier for the Nobel Laureate
	

- `full_name`: The full name of the Nobel Laureate
	

- `gender`: The gender of the laureate (`female`, `male` and `org` for organizations)

- `born_date`: The birth year of the laureate
	
- `born_country`: The country where the laureate was born
	
- `born_city`: The city where the laureate was born
	

- `died_date`: The year of death of the laureate (if applicable; `NA` means that the lareate is alive or it was an organization)
	
- `died_country`: The country where the laureate died (if applicable)
	
- `died_city`: The city where the laureate died (if applicable)
	
- `organization_name`: The name of the organization the laureate is associated with
	
- `organization_country`: The country where the associated organization is located
	
- `organization_city`: The city where the associated organization is located (if applicable)

-----------------------------------------------


## Solutions:



::: {#sol-1}

We can list the number of rows (observations) and columns (variables) with ...

```{r}

```

Each row represents ...

:::




::: {#sol-2}


```{r}
#| label: living
#| eval: false
nobel_living <- nobel |>
  filter(
    !is.na(organization_country),
    gender __ "org",
    ___(died_date)
  )



```


>  Don't forget to remove the chunk option `eval: false` after replacing the placeholder with the appropriate code. Otherwise, the code will not be evaluated.

:::



------

First, we'll create a new variable to indicate whether the laureate was in the U.S. when they won their prize. 


```{r}
#| label: living-us
#| eval: false
nobel_living <- nobel_living  |> 
  mutate(
    country_us = if_else(organization_country == "USA", 
                         "USA", "Other")
  )
```

Next, we will limit our analysis to only the following categories: `physics`, `medicine`, `chemistry`, and `economic`.

```{r}
#| label: ph-med-chem-eco
#| eval: false
nobel_living_science <- nobel_living |>
  filter(category %in% c("physics", "medicine", "chemistry", "economics"))
```


> Don't forget to remove the chunk option `eval: false`. Otherwise, the code will not be evaluated.

-----


::: {#sol-3}


```{r} 
#| label: barplot
#| eval: false
ggplot(nobel_living_science, aes(___ = country_us) ) +
  ___() +
  facet_wrap( ~ ___)
```


>  Don't forget to remove the chunk option `eval: false` after replacing the placeholder with the appropriate code. Otherwise, the code will not be evaluated.

:::




::: {#sol-4}


We start with creating the variable `born_country_us`. 


```{r}
#| label: born-country
#| eval: false
nobel_living_science <- nobel_living_science |>
  mutate(
    _____ 
    )

```

Now we can count the number of winners born in US ...

```{r}
#| label: count-born-us
#| eval: false
nobel_living_science |>
  ___
```

> Don't forget to remove the chunk option `eval: false` after replacing the placeholder with the appropriate code. Otherwise, the code will not be evaluated.

:::



::: {#sol-5}


```{r}
#| label: barplot2
#| eval: false
ggplot(nobel_living_science, 
       aes(___ = country_us, ___ = born_country_us) ) +
  ___() +
  facet_wrap( ~ ___) +
  ___
``` 

> Don't forget to remove the chunk option `eval: false` after replacing the placeholder with the appropriate code. Otherwise, the code will not be evaluated.

In all four categories, ...

:::



::: {#sol-6}



> Now you have to add the code chunk on your own.


:::




::: {.callout-note icon=false}

After completing your solution, delete this note and any other notes instructing you to remove the `eval: false` chunk option.

:::  


