---
title: "Monte Carlo simulations"
format: 
  html:
    embed-resources: true
---



::: {.callout-note icon=false}

Ensure that you remove `eval: false` or change it to `eval: true` before you render your final submission.


:::  



## The birthday problem



::: {#sol-1}


The first step is to define a function that runs the experiment once.

```{r}
#| eval: false
same_birthday <- function(n){
  n_same_birthday <- ____ |> 
    duplicated() |> 
    sum()
  
  result <- ifelse(n_same_birthday ___, TRUE, FALSE)
  return(result)

}

```


Next, repeat the experiment `B` times to obtain a distribution of outcomes.

```{r}
#| eval: false
set.seed(1)
B <- 10000
____



```



The estimated probability is then ....


:::  





::: {#sol-2}
Let $A_i$ be the event that person $i$ has a unique birthday. Then
$$A_1 \cap A_2 \cap \cdots \cap A_{50}$$

represents the event in which all 50 individuals have unique birthdays. …

:::  




## The Monty Hall Problem



::: {#sol-3}

The following function, `stick()`, simulates the outcome of using the stick strategy.

```{r}
#| eval: false
stick <- function(){
  doors <- as.character(1:3)
  prize <- sample(c("car", "goat", "goat"))
  prize_door <- doors[ ___ ]
  my_pick  <- sample(doors, 1)
  show <- sample(doors[
    ___ %in% c(my_pick, prize_door)
    ], 1)
  stick <- my_pick   # we don't change the decision
  stick == prize_door
}
```

Now we can use `stick()` to run the Monte Carlo simulation.

```{r}
set.seed(1)

```



:::  







## Sampling Models





::: {#sol-4}

```{r}
#| eval: false
set.seed(1)
n <- 500
B <- 10000

___
```


:::  





::: {#sol-5}

```{r}
#| eval: false

library(tidyverse)

data.frame(earnings = earnings) |> 
  ___
```




The probability of losing money is ....


```{r}

```

:::