---
title: "Predictors associated with infant birth weight"
format: 
  html:
    embed-resources: true
---


### Packages

```{r}
#| eval: false
#| message: false
library(tidyverse)

```


### Data preprocessing

```{r}
#| eval: false
penguins <- penguins |>
  drop_na() |>
  mutate(large = factor(if_else(body_mass > mean(body_mass, na.rm = TRUE), 1, 0)))
```


#### a)


```{r}
#| eval: false
ggplot(penguins, ) +

```



#### b)


The probability that a randomly selected Adelie penguin is large is given by: 
```{r}
#| eval: false
penguins |> 
  filter(species == "Adelie") |> 

```


The odds that a randomly selected Adelie penguin is large is given by: 

```{r}
#| eval: false
penguins |> 
  filter(species == "Adelie") |> 

```




#### c)

We split the data into training and test part by using functions from tidymodels.

```{r}
#| eval: false
library(tidymodels)
set.seed(12345)
penguins_split <- 
penguins_train <- 
penguins_test <- 
```


Now we can fit the model to the training data.

```{r}
#| eval: false

model_s <- glm(large ~ )

```


The predicted odds can be computed using ...


```{r}
#| eval: false

# computing probabilities
pi_g <- predict(model_s, )

pi_a <- predict(model_s, )

# computing the odds

```


#### d)





#### e)


```{r}
#| eval: false

model_sf <- 
  

```



To compute the change in the odss, we need the estimated slope of `flipper_len`. ...

```{r}


```


#### f)


We compute predictions for the test data

```{r}
#| eval: false 
pred_s <- predict(model_s, )
pred_sf <- predict(model_sf, )

```

Given those predictions, we can compare them with the actually observed values of `large` in the test data. Based on that comparison we can computed the ROC curve using ...

```{r}
#| eval: false
roc_s <- 
roc_sf <- 
```


The two ROC curves are then plotted into one figure with the `ggroc()` function.

```{r}
#| eval: false
bind_rows(roc_s, roc_sf, .id = "model") |>
  group_by(model) |>
  ggplot(aes(x = 1- specificity, y = sensitivity, color = model)) + 
  geom_path() +
  scale_color_brewer(palette = "Set1", name = "model",
                     labels = c("species", "specie + flipper length"))

```

#### g)

The auc values are:


```{r}

```


`roc_s` and `roc_sf` contain specificity and sensitivity values for different thresholds. 


```{r}
#| eval: false
roc_s |> 
  # Calculate Youden's J for every row in the ROC curve
  mutate(j_index =  ) |> 
  # Grab the row where J is maximized
  ___
  

roc_sf |> 
  # Calculate Youden's J for every row in the ROC curve
  mutate(j_index =  ) |> 
  # Grab the row where J is maximized
  ___

```



