---
title: "Real Estate Prices"
format: 
  html:
    embed-resources: true
---


## Objective

This assignment involves analyzing a real estate dataset to practice fitting, interpreting, and selecting linear regression models.



::: {.callout-note appearance="simple" icon=false}


::: {.remark} 
Begin by rendering the Quarto file to verify that an HTML file can be created. Ensure that the option `embed-resources: true` in the YAML header remains unchanged.

```
format: 
  html:
    embed-resources: true
```

Otherwise, the HTML file uploaded to Moodle may be incomplete and could lack essential components such as figures.

Proceed through each exercise sequentially. Upon completion of an exercise, remove the `eval: false` code chunk option if present. Otherwise, the code will not be evaluated and the results will not appear in the HTML output. Replace all placeholders (___) with the appropriate text or code.
Generate the HTML output after completing each exercise to verify that results are rendered correctly. This remark may be removed upon finalizing the solution.

:::


:::  

#### Packages

The **tidyverse** package will be used for data manipulation, visualization, and data import, while the `tidy()` function from the `broom` package will be used for summarizing model outputs. Both packages can be loaded using the following code:
```{r}
#| label: load-packages
#| message: false
#| eval: false
library(tidyverse)
library(broom)
```



## Dataset


The dataset is provided in the file `real_estate.csv`, which is available on Moodle in the folder *Data files, Quarto files and Solutions to previous problem sets*.

It contains 500 observations of houses with the following variables:

- `price`: House price in thousands of euros.

- `size`: Size of the house in square meters.

- `bedrooms`: Number of bedrooms.

- `bathrooms`: Number of bathrooms.

- `age`: Age of the house in years.

- `location`: Location of the house (categorical: `Urban`, `Suburban`, `Rural`).

- `has_garden`: Whether the house has a garden (`Yes`/`No`).

- `has_garage`: Whether the house has a garage (`Yes`/`No`).




## Solutions

Begin by reading the data. Save the starter file `starter_real_estate.qmd` in a designated folder. Create a subfolder named `data` within this folder to enable reading the `real_estate.csv` file using the following command.





```{r}
#| label: readin-data
#| message: false
#| eval: false

real_estate <- read_csv("data/real_estate.csv")
```

Examine the structure and contents of the dataset.

```{r}
#| eval: false

real_estate
```





::: {#sol-1}



The figure indicates the following:





```{r}
#| eval: false
real_estate |> 
  ggplot(mapping = aes(___)) +
  geom_point() + 
  ___ +
  labs(
      ___
    ) +
  scale_color_gradient(___) +
  theme_minimal()

```

___ demonstrates the strongest association with `price` ...


:::




::: {#sol-2}


```{r}
#| eval: false

# Fit the model
model_simple <- 
  
# View the fitted model
tidy(model_simple)
```


...

:::



::: {#sol-3}

```{r}
#| eval: false

# Fit the model
model_multiple <- 
  
# View the fitted model
tidy(model_multiple)
```


...

:::




::: {#sol-4}

`location` can be transformed into a factor variable ...

```{r}
#| eval: false

real_estate <- real_estate |> 
  mutate(location = ___)
```

Since dummy coding is the default ...

```{r}
#| eval: false

# Fit the model with location
model_location <- 
  
# View the fitted model

```


...

:::




::: {#sol-5}

```{r}
#| eval: false

# Fit the model with binary predictors
model_binary <- 
  
# View the fitted model

```


...

:::




::: {#sol-6}

```{r}
#| eval: false
# Fit the model with interaction
model_interaction <- 
  
# View the fitted model


```


...

:::




::: {#sol-7}

```{r}
#| eval: false
# Calculate adjusted R-squared for each model
adj_r2_simple <- summary(model_simple)$___

adj_r2_multiple <- 
  
adj_r2_int <- 
  

```


...


:::






::: {#sol-8}

```{r}
#| eval: false

set.seed(2026)
n <- nrow(real_estate)
train_id <- sample(1:n, floor(0.9 * n))  # split 90/10
train <- real_estate[train_id, ]
test <- real_estate[-train_id, ]
```


...

```{r}
#| eval: false

model_multiple_train <- 
  
model_int_train <- 
  

```


Given the fitted models from the previous step, we can predict house prices for the new observations contained in `test`. ...


```{r}
#| eval: false

pred_multiple <- 
  
pred_int <- 
  
```

The root mean squared error can be computed in the following way:

```{r}
#| eval: false

model_multiple_MSE <- sqrt(mean(___))
model_int_MSE <- 
  
```

...

:::



